Very Preliminary Draft

### 2021-07-05 article/draft.tex
n-th update

{\color{pink} Finally, we found irregularities in the number of Infowars articles collected from Buzzsumo. While Infowars usually publishes $20$ to $30$ articles per day, only $53$ articles were collected in the $31$-day period between June $11$ to July $11$, 2020. A temporary crawling problem coming from Buzzsumo may have caused this lack of data. Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.}

@@

We further examine the placement of interstitials that indicate a possibly sensitive content. We find that only $2.97\%$ out of $323$ $938$ tweets containing a URL marked as False, have an interstitial ``potentially sensitive content''. In particular, many speak about COVID19 and do not contain a label to provide users with more context from authoritative sources. Figure \ref{fig_notice} provides an example of a tweet sharing a URL marked as False by a Fact-checker and which contains an interstitial ``potentially sensitive content''. We find 32 other tweets, among our set of collected tweets, who share the exact same URL link in our the previous example and among those 32 only 5 tweets had the interstitial ``potentially sensitive content''. Again this points towards the non-automation of the interstitials placement.

@@

\begin{table}[] 
\begin{tabular}{|c|c|c|c|c|}
\hline
Category       & \begin{tabular}[c]{@{}c@{}}With information \\ panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Without Information \\ panel\end{tabular} & Total & \begin{tabular}[c]{@{}c@{}}IP\\ percentage\end{tabular} \\ \hline
General Health & 0                                                                 & 11                                                                   & 11    & 0                                                       \\ \hline
Vaccine        & 21                                                                & 7                                                                    & 28    & 75                                                      \\ \hline
COVID          & 73                                                                & 43                                                                   & 116   & 63                                                      \\ \hline
Climate change & 5                                                                 & 13                                                                   & 18    & 28                                                      \\ \hline
\end{tabular}
\caption{}
\label{tab2}
\end{table}

@@

{ \color{pink}

@@

\end{itemize}
}

>>>>

@@

We further examine the placement of interstitials that indicate a possibly sensitive content. We find that only $2.97\%$ out of $323$ $938$ tweets containing a URL marked as False, have an interstitial ``potentially sensitive content''. In particular, many speak about COVID19 and do not contain a label to provide users with more context from authoritative sources. Figure \ref{fig_notice} provides an example of a tweet sharing a URL marked as False by a Fact-checker and which contains an interstitial ``potentially sensitive content''. We find 32 other Tweets, among our set of collected tweets, who share the exact same URL link as in the previous example. Among those 32 Tweets, only 5 tweets had the interstitial ``potentially sensitive content''. Again this points towards the non-automation of the interstitials placement.

@@

\begin{table}[] 
\begin{tabular}{|c|c|c|c|c|}
\hline
Category       & \begin{tabular}[c]{@{}c@{}}With \\ information \\ panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Without  \\\ information \\ panel\end{tabular} & Total & \begin{tabular}[c]{@{}c@{}}IP \% \end{tabular} \\ \hline
\begin{tabular}[c]{@{}c@{}} General \\ Health \end{tabular} & 0                                                                 & 11                                                                   & 11    & 0                                                       \\ \hline
Vaccine        & 21                                                                & 7                                                                    & 28    & 75                                                      \\ \hline
COVID19          & 73                                                                & 43                                                                   & 116   & 63                                                      \\ \hline
\begin{tabular}[c]{@{}c@{}}  Climate \\ change \end{tabular} & 5                                                                 & 13                                                                   & 18    & 28                                                      \\ \hline
\end{tabular}
\caption{}
\label{tab2}
\end{table}

@@

{ \color{pink} 
Sporadic points for the discussion, no structure yet.

@@

	\item Finally, we found irregularities in the number of Infowars articles collected from Buzzsumo. While Infowars usually publishes $20$ to $30$ articles per day, only $53$ articles were collected in the $31$-day period between June $11$ to July $11$, 2020. A temporary crawling problem coming from Buzzsumo may have caused this lack of data. Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible. 
\end{itemize}
}
